Concurrent Programming in Harmony

### 2021-08-14 book/paper.tex
Latest

@@

>>>>

The model checker also counts the number of times each \textbf{Possibly}
instruction is invoked with the value \textbf{True}.  It reports those
\textbf{Possibly} instructions that either have never been reached or
never have been executed with the value \textbf{True}.

@@

You can see if you are running the latest version of Harmony at any
time by running \texttt{Python3 install.py --check}.  If you would like
to update your installation, run \texttt{Python3 install.puy --update}.
